### 2016-12-09 Hhh/Hhh.tex
Adding part of jets section

In this method a demotion or promotion probability is assigned to every
jet as in equation \ref{eqn:promotedemote}.
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1}
\end{align}
In this equation $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
under consideration.

>>>>

In this method a demotion or promotion probability is assigned to every
jet as:
\begin{align}\label{eqn:promotedemote}
&P(\text{demote}) = 1 - SF \text{  for SF < 1 }  \notag \\
&P(\text{promote}) = \frac{(SF - 1)(\epsilon_{\text{MC}}-1)}{SF} \text{    for SF > 1},
\end{align}
Where $SF$ is the scale factor mentioned above, and $\epsilon_{\text{MC}}$ is
the b--tagging efficiency in \ac{MC} events for the type of jet (light, b- or c-)
under consideration.

### 2016-12-09 Objects/Objects.tex
Adding part of jets section

\section{Jets and b-tagging}
\label{sec:objects_jets}

@@

>>>>

\section{Jets and b-tagging}
\label{sec:objects_jets}
Many quarks and gluons are produced in the collisions at the \ac{LHC},
fragmenting and hadronising immediately and forming collimated
jets of particles. These particle jets need to be combined
into single objects so the properties of the original particles can
be measured.

The particles identified by the \ac{PF} algorithm
are clustered into jets using the anti-\kT algorithm \cite{antiKT} as implemented
in \texttt{FastJet} version 3.0.1 \cite{fastjet}. Jet clustering algorithms 
define distance parameters $d_{ij}$, denoting the distance between object (particle or cluster of 
particles) $i$ and 
object $j$, and $d_{iB}$ denoting the distance between 
object $i$ and the beam. The smallest of the distances
is defined and if this is a distance between object i and an object j, objects
i and j are combined. If $d_{iB}$ is the smallest distance, object i
is called a jet and removed from the list of objects. In the anti-\kT algorithm
these distance parameters are defined as:
\begin{align}\label{eqn:objects_antikt}
d_{ij}=\text{min}(p_{\text{T},i}^{-2},p_{\text{T},j}^{-2})\frac{\Delta_{ij}^2}{R^2}\\
d_{iB} = p_{\text{T}}^{-2},
\end{align}
where $\Delta_{ij} = \sqrt{(y_i-y_j)^2+(\phi_i - \phi_j)^2}$ is the distance
between the objects i and j in rapidity-azimuthal angle space. The radius
parameter $R$ was chosen as 0.5 during Run 1 CITATION and as 0.4 during Run 2 \cite{cms-jets-run2}. 
This algorithm is collinear-- and infrared--safe, which means that the number of jets
is not affected by the emission of soft collinear gluons or parton splitting. 
The effects of pile--up particles on the jet energy and substructure can be
mitigated using several methods. For the analysis presented in CHAPMSSM a
\ac{CHS} technique is employed \cite{cms-jets-run2}.  In this method
charged hadronic \ac{PF} candidates not associated with the primary vertex 
are not considered in the clustering. For the analysis presented in
chapter \ref{chap:hhh} a dedicated identification algorithm \cite{cms-jets-puid} 
based on vertex- and jet shape information was used to reject jets due to pile--up.

@@

\subsection{B-tagging}
\label{sec:objects_jets_btag}
